Bayesian Nonparametric System Reliability\\ using Sets of Priors

### 2016-01-31 ijar-npb-ms.tex
acknowledgements Gero
Abstract and intro (done but maybe incomplete if too compact?)  Lots of text left lying round in intro until decision if it is ok or not.

\begin{abstract}
Imprecise Bayesian nonparametric approach to system reliability with multiple types of components,
sets of priors through sets of canonical parameters,
leading to sets of system reliability functions,
reflection of prior-data conflict
\end{abstract}

@@

(some sentences may be useful for the abstract instead)

System with components of $k=1,\ldots,K$ different types.
There are $m_k$ components of type $k$ in the system.
Components of the same type are i.i.d.\ and independent of components of other types.
Arbitrary system layout, i.e.\ any series / parallel combination, $k$ out of $n$ etc.

@@

Based on expert assumptions for component failure distributions and component test data,
we make predictive inference for a system with components that are exchangeable
with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
naturally a Bayesian model for the functioning probability at each time point arises (see Section~\ref{sec:nonparamapproach}).
To account for uncertainty in the choice of prior
and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
we propose an imprecise probability approach
based on sets of prior distributions defined through sets of canonical parameters.
This approach also allows to adequately model weak or partial prior information.
In particular, prior near ignorance can be modelled much more naturally than through usual so-called noninformative priors.

@@

\td{***illustrate discrete distribution with a graph of R, f, h?***}

@@

\section{Practical Usage and Examples}

%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},

@@

In this paper we have contributed an imprecise Bayesian nonparametric approach
to system reliability with multiple types of components.
The approach allows modeling partial or imperfect prior knowledge on component failure distributions
in a flexible way through bounds on the functioning probability for a grid of time points, 
and combines this information with test data in an imprecise Bayesian framework.
Component-wise predictions on the number of functioning components
are then combined to bounds for the system survival probability by means of the survival signature.
New results on first-order stochastic dominance for the Beta-Binomial distribution
enable closed-form solutions for these bounds in most cases and 
avoid exponential growth in the complexity of computing the estimate
as the number of components grows.
The widths of the resulting system reliability bounds
reflect the amount of test data, the precision of prior knowledge,
and crucially provide an easily used method to identify 
whether these two information sources are in conflict in a
way which is of consequence to the whole system reliability
estimate.

>>>>

\begin{abstract}
An imprecise Bayesian nonparametric approach
to system reliability with multiple types of components
is developed.
This allows modelling partial or imperfect prior knowledge on component failure distributions
in a flexible way through bounds on the functioning probability.
Given component level test data these bounds are propagated 
to bounds on the posterior predictive distribution for the reliability of
a new system containing components exchangeable with those 
used in testing.  The method further enables identification 
of prior data conflict at the system level based on component level test data.

There are new results on first-order stochastic dominance for the Beta-Binomial distribution
which make the technique computationally tractable.  These methodological contributions can be immediately used in
applications by reliability practitioners using the freely available
software tools which are provided.
\end{abstract}

@@

A critique of the methodological approach to a reliability 
analysis may often encompass a few common concerns.
First, in a parametric 
setting, there may be no particularly strong reason to
believe that the small part of component model
space covered by a particular probability distribution 
necessarily contains the `true' component lifetime distribution.
Further, Bayesian methods may be invoked in order to 
incorporate expert opinion or other knowledge which falls
outside the specific testing data under consideration.  The 
classic concern here is in whether one can truly express 
ones beliefs with the exactness a prior requires.  Finally,
it would be valuable in application to have a means of identifying when the
prior choice is having a strong effect and when not.  Any method 
hoping to address these concerns must do so whilst enabling 
realistic system models (with heterogeneous component types)
and remain computationally tractable.

Herein, we make steps toward addressing these concerns by developing
a nonparametric method which utilises imprecise probability 
to encapsulate more vague or imperfect prior beliefs using
upper and lower probabilities.  This overcomes the concern
about component lifetimes being outside a particular 
parametric family, uses a more flexible prior modelling 
framework and leads to an easy method of detecting prior-data
conflict which should be of concern at the system level.

Furthermore, the method is based on the survival signature, a 
recent development which naturally accommodates 
heterogeneous component types laid out in any arbitrary
manner which maintains coherency of the system.  As will be 
seen in the sequel, the method remains computationally tractable.

\td{*** Some more words on the benefits?}

In Section \ref{sec:survsign} we review the survival 
signature and in Section \ref{sec:nonparamapproach} we 
review the nonparametric approach to Bayesian reliability analysis
upon which our work builds 
\cite{2015:bayessurvsign}.  Section \ref{sec:reparam} details
the reparameterisation of that approach which enables the natural
formulation of the system reliability bounds and which leads to
nice closed form results in some later theory.
Section \ref{sec:setsofbetapriors} lays the ground work to incorporate imprecise probability,
culminating in the main results and contributions of this 
work, detailed in Section \ref{sec:setsofrel}.  Section 
\ref{sec:examples} provides details on the software contributions
of this work and shows two worked examples
demonstrating the practicality and usefulness of the method.

\td{*** LOUIS: Not sure if the above is too compact or ok and whether we need to be more expansive in the orange bit above?  Thoughts appreciated! I've left text below which you may want to draw from? ***}

@@

Based on expert assumptions for component failure distributions and component test data,
we make predictive inference for a system with components that are exchangeable
with the test components by calculating the system reliability function $\Rsys(t) = P(\Tsys > t)$.
Considering a discrete grid of time points $\{t_1, \ldots, \tmax\}$,
a Bayesian model for the functioning probability at each time point naturally arises (see Section~\ref{sec:nonparamapproach}).
To account for uncertainty in the choice of prior
and due to the inherent issue with prior-data conflict (see below / Section~\ref{sec:reparam}),
we propose an imprecise probability approach
based on sets of prior distributions defined through sets of canonical parameters.
This approach also allows to adequately model weak or partial prior information.
In particular, prior near ignorance can be modelled much more naturally than through usual so-called noninformative priors.

@@

@@

\section{Practical Usage and Examples}
\label{sec:examples}
%***code published in Louis' \textbf{R} package \texttt{ReliabilityTheory},

@@

In this paper we have contributed an imprecise Bayesian nonparametric approach
to system reliability with multiple types of components.
The approach allows modelling partial or imperfect prior knowledge on component failure distributions
in a flexible way through bounds on the functioning probability for a grid of time points, 
and combines this information with test data in an imprecise Bayesian framework.
Component-wise predictions on the number of functioning components
are then combined to bounds for the system survival probability by means of the survival signature.
New results on first-order stochastic dominance for the Beta-Binomial distribution
enable closed-form solutions for these bounds in most cases and 
avoid exponential growth in the complexity of computing the estimate
as the number of components grows.
The widths of the resulting system reliability bounds
reflect the amount of test data, the precision of prior knowledge,
and crucially provide an easily used method to identify 
whether these two information sources are in conflict in a
way which is of consequence to the whole system reliability
estimate.
